\input{utilities}

\def\firstname{Sayed}
\def\lastname{Ahmed}
\def\email{sayeed205@gmail.com}
\def\linkedin{linkedin.com/in/sayeed205}
\def\github{github.com/sayeed205}
\def\jasphone{+919851305775}

% \def\jbegin{\begin{itemize}}
% \def\jitem{\item }
% \def\jend{\end{itemize}}
\def\jbegin{\resumeItemListStart}
\def\jitem{\resumeItem}
\def\jend{\resumeItemListEnd}

\def\profileSummary{
\section{Career summary so far}
Full-stack developer specializing in Node.js, AdonisJS, React, Inertia.js, and PostgreSQL, with hands-on experience building SaaS platforms, admin dashboards, authentication systems, and production-ready business applications. Skilled in backend architecture, database design, type-safe development, and end-to-end delivery through internships, freelance work, and personal projects.
}


\def\achievements{
    \jbegin
        \jitem{\lrand[1]}
        \jitem {\lrand[2]}
        \jitem {\lrand[1]}
        \jitem {\lrand[2]}
    \jend
}

% # Add education item here
\EducationTemplate{College}
{Aug 2020}{Jul 2024}
{Camellia Institute of Technology and Management}
{B. Tech}
{CSE - 9.4 CGPA}

\ExpTemplate{IncubatorOp}
{Aug 2024}
{Sept 2024}
{Full-Stack Developer}
{\href{https://incubator-op.vercel.app}{IncubatorOP}}
{On Site}
{
\jbegin
    \jitem{Spearheaded the development of \href{https://teacherop.com}{teacherop.com}, an AI-driven platform designed for seamless text-based course and assessment creation.}
    \jitem{Architected and implemented the entire system from scratch, integrating AI tools to streamline content generation and evaluation processes.}
\jend
}

\ExpTemplate{UnocoGlobal}
{Dec 2022}
{Feb 2023}
{Backend Developer Intern}
{\href{https://www.unicoglobal.in}{Unico Global}}
{Remote}
{
\jbegin
    \jitem{Led backend development for a closed community social \href{https://www.unicoglobal.in/portfolio/take-off-with-tami-community-mobile-web-app}{media chatting app}, serving over 5,000 active users.}
    \jitem{Engineered Chrome extensions to scrape user information from 1,000+ Slack workspace members and 500+ LinkedIn connections, aiding data collection for marketing teams.}
\jend
}

\ExpTemplate{Dukaan}
{Oct 2023}
{Mar 2024}
{Backend Developer Intern}
{\href{https://mydukaan.io}{Dukaan}}
{On site}
{
\jbegin
    \jitem{Enhanced performance of \href{https://bot9.ai}{BOT9.AI} by integrating plugins for platforms including Slack, Discord, Intercom, Freshdesk, Zendesk, and Meta Messenger.}
    \jitem{Optimized SQL queries, reducing response time by 70\% (from 15s to 800ms) for fetching 10,000 user-bot conversations.}
    \jitem{Implemented WebSocket features for real-time communication, improving user engagement.}
\jend
}

\HckTemplate{wanderfly}
{}
{\href{https://www.wanderfly.in}{Wanderfly.in}}
{AdonisJS, React, Inertia, Tailwind CSS, PostgreSQL, Slack API}
{\jbegin
    \item{Freelance full‑stack project: built \textbf{Wanderfly}, a SaaS workplace wellbeing platform offering mood tracking, stress check‑ins, AI‑therapy chat, and personalized wellness programs.}
    \item {Integrated seamless experience via \textbf{Slack}, enabling anonymous pulse checks, stress dashboards, team leaderboards, and real‑time manager alerts.}
    \item {Delivered a 25\% reduction in HR stress and 10\% increase in employee engagement within three months at a client firm; estimated turnover‑cost savings ₹4K per head.}
    \item {Enabled HR analytics and trend reporting through gamified streak tracking and well‑being dashboards to support proactive interventions.}
\jend}

\HckTemplate{hsmjewellers}
{}
{\href{https://hsmjewellers.com}{HSM Jewellers}}
{AdonisJS, React, Inertia, Tailwind CSS, PostgreSQL, R2}
{\jbegin
    \item{Freelance full‑stack project: built \textbf{HSMJewellers}, a full-stack network marketing/MLM jewellery platform to manage member onboarding, referral-tree structures, gold wallet purchases, EMI plans, rewards, withdrawals, and admin workflows.}
    \item {Implemented scalable MLM backend workflows including live gold-rate fetching with caching, recursive downline/upline processing, queue-based achievement calculations, and scheduled salary/reward computation.}
    \item {Integrated production-ready financial and compliance features such as GST-aware PDF invoices, KYC/bank document uploads, Cloudflare R2/S3-compatible storage, Redis caching, and transaction-linked audit documentation.}
\jend}

\HckTemplate{letsgo}
{}
{\href{https://www.exploreletsgo.com}{Lets GO}}
{AdonisJS, React, Inertia, Tailwind CSS, PostgreSQL, Kotlin, MDY, Android}
{\jbegin
    \item{Freelance full‑stack project: Led end-to-end development of an internal travel operations platform across Android and backend services, helping staff manage customers, tours, invoices, vouchers, receipts, and reminders from one workflow.}
    \item {Built a typed client-server integration using backend OpenAPI documentation with Android Retrofit/Moshi code generation, reducing API mismatch issues and speeding up feature delivery.}
    \item {Implemented production-ready reminder and document workflows, including scheduled backend notification jobs, Firebase Cloud Messaging push alerts, offline voucher draft storage, and branded PDF voucher/receipt generation.}
\jend}

\HckTemplate{ankusfood}
{}
{\href{https://ankusfood.com}{Ankus Food}}
{AdonisJS, React, Inertia, Tailwind CSS, PostgreSQL}
{\jbegin
    \item{Freelance: Built a full-stack internal operations platform for a multi-outlet food company centralizing staff, kitchen/outlet, and admin workflows.}
    \item {Implemented workforce management features including staff assignment, outlet transfers, resignation tracking, active/resigned filters, and manager-scoped access control.}
    \item {Developed a secure role-based dashboard with outlet KPIs, staff analytics.}
\jend}


% \DefineArrayVar{Education}{@}
% {,}{School, Course, Stream, Start, End}
% {,}{C,D}


% % # Add experience item here




% \renewcommand{addEducation}{}


% # Add projects here
